---
title: "Network"
author: "Taehee Kim"
date: "12/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this example we use following libraries. Install the libraries in case you have not before.
We also collect Twitter data using `rtweet`. So make sure you have your twitter token in your system. 

```{r, eval = TRUE, message = FALSE}
library(rtweet)
library(dplyr)
library(plotly)
library(igraph)
library(RColorBrewer)

# Create twitter token
source("0_token.R")

```


```{r, eval = FALSE}
# In case you don't have above packages..
install.packages("package.name")
```

In this exampel we tweets containing two keywords "rigged" and "election". This will take about an hour. 
Q. Why?
```{r, eval = FALSE}
# Data collection
rigged <- search_tweets(q = "rigged election", 
                        n = 72000, 
                        retryonratelimit = TRUE,
                        since = "2020-12-03", 
                        until = "2020-12-05")
```

```{r, eval = TRUE, echo = FALSE}
load("search_rigged_election_20201204.RData")
load("rigged_election_network2.RData")
```

Check collected data.
```{r, eval = TRUE}
dim(rigged)
head(rigged)[,1:5]

min(rigged$created_at)
max(rigged$created_at)
```

Now let's create a graph object using the data.
```{r, eval = TRUE}

# Create graph object -----------------------------
t_rt <- rigged %>%
  filter(is_retweet == 'TRUE') %>%
  select(user_id,retweet_user_id,screen_name, retweet_screen_name, verified, retweet_verified)


t_rt <- as.matrix(t_rt)

# edges
edges <- t_rt[,c(1,2)]
head(edges)

# actors
actors <- rbind(t_rt[,c(1,3,5)], t_rt[,c(2,4,6)])
head(actors)

# Check if there are duplicated user_ids
table(duplicated(actors[,1]))
length(unique(actors[,1]))

# Remove duplicated ones
dup <- duplicated(actors[,1])
actors <- actors[!dup,] # ! is negation.
```

```{r, eval = FALSE, echo= TRUE}
# Create a graph object using igraph function
g <- graph_from_data_frame(edges, directed=TRUE, vertices = actors)
```

```{r, eval = TRUE}
# Check graph object
summary(g)
```


```{r, eval = TRUE}
# Check Edges and nodes
V(g)
E(g)

head(V(g)$screen_name)
head(V(g)$verified)
```


Let's check if Donald Trump's node is existed in our network.
```{r, eval = TRUE}
# Finding Donald Trump
trump_v <- which(V(g)$screen_name == "realDonaldTrump")
trump_v

# Trump degree
degree(g, v = trump_v)
# Trump indegree
degree(g, v = trump_v, mode = "in")
# Trump outdegree
degree(g, v = trump_v, mode = "out")
```



## Centrality 
Here we calculate three centrality measures: degree, betweenness, closeness. Other centrality can be measured using igraph function. For more detail, check its documentation.
```{r, eval = TRUE}

# degree
head(degree(g))

# Plot the degree distribution in a log-log plot
plot(degree.distribution(g), log = "xy")

# Let's write the degree as a node attribute:
V(g)$degree <- degree(g)
V(g)$indegree <- degree(g, mode="in") # The same can be done for in-degree:
V(g)$outdegree <- degree(g, mode="out") # and out-degree


# Chek top 10 nodes by its degree
V(g)[order(-degree)]$degree[1:10]
V(g)[order(-degree)]$screen_name[1:10]

# Also check is those accounts are verified one or not
V(g)[order(-degree)][1:10]$verified

# Also indegree
V(g)[order(-indegree)][1:10]$screen_name
V(g)[order(-indegree)][1:10]$verified
```


```{r, eval = FALSE}
# Closeness and Betweenness
# It can take couple of minutes!
V(g)$closeness <- closeness(g, mode = "all") # "all" uses undirected pass.
V(g)$between <- betweenness(g, directed = FALSE)
```

```{r, eval = TRUE}
# Check top 10 nodes by two centrarity measures
V(g)[order(-closeness)]$screen_name[1:10]
V(g)[order(-between)]$screen_name[1:10]
```


## Plot graph
Lets plot our retweet network. igraph does not plot well when it has more than 1,000 of nodes.
So in this example, we plot a small subset of the graph. 
```{r, eval = TRUE}
# simple plot

# Set node color
V(g)$color <- rgb(239, 249, 222, maxColorValue = 255) # light green

# Get top nodes
top_nodes <- V(g)[order(-degree)][1:500]

# Create a small graph 
small.g <- delete.vertices(g, which(!V(g) %in% top_nodes)) # delete nodes if those are not included in 'top_nodes'

# Layout setting. We use Fruchterman Rheingold algorithm for network layout.
lay <- layout_with_fr(small.g)

small.g <- simplify(small.g)
plot(small.g, 
     vertex.label = NA, 
     vertex.size = 5,
     edge.arrow.size = 0.1, 
     edge.arrow.width = 0.3,
     vertex.color = V(small.g)$color,
     layout = lay)



# Plot: Set color ----------------------

# add color

# base color2 # light green
V(g)$color2 <- rgb(239, 249, 222, maxColorValue = 255) 



# Add red color to @realDonaldTrump and nodes who retweeted realDonaldTrump
ok <- V(g)$screen_name == "realDonaldTrump"
V(g)$color2[ok] <- (rgb(255,179,186, maxColorValue = 255)) # red
ok2 <- neighbors(g, ok, mode = "in")
V(g)$color2[ok2] <- (rgb(255,179,186, maxColorValue = 255))

# Add blue color to @BernieSanders and nodes who retweeted BernieSanders
ok <- V(g)$screen_name == "BernieSanders"
V(g)$color2[ok] <- rgb(186,225,255, maxColorValue = 255) # blue
ok2 <- neighbors(g, ok, mode = "in")
V(g)$color2[ok2] <- rgb(186,225,255, maxColorValue = 255)


# check 
table(V(g)$color2)


# Lets plot again.

top_nodes <- V(g)[order(-degree)][1:500]
small.g <- delete.vertices(g, which(!V(g) %in% top_nodes))
lay <- layout_with_fr(small.g)


small.g <- simplify(small.g)
plot(small.g, 
     vertex.size = 5,
     edge.arrow.size = 0.1, 
     edge.arrow.width = 0.3,
     vertex.label = NA,
     vertex.color = V(small.g)$color2,
     layout = lay
     )

mtext("Top 500 users by degree", side = 1)

```


## Clustering
It looks like this network has some clusters. Lets figure out clusters using fast greedy algorithm here. Note that it might take couple of minitues to get the results.
```{r, eval = FALSE}
un_g <- as.undirected(g) # it should be undirected graph
un_g <- simplify(un_g) # remove redundent edges

# Fast greedy algorithm
fg <- cluster_fast_greedy(un_g)
```


```{r, eval = TRUE}
# Check how many clusters are detected
length(fg)

# Check sizes of the clusters
head(sizes(fg), 30)

# Check modularity
modularity(fg)

# Check which nodes belongs to which clusters
head(membership(fg))
```

The algorithm detects about 700 clusters. But lets look into large clusters which consists more than 1000 nodes.

```{r, eval=TRUE}

# We use community, 1,2,3,4,5,8,12 
# check plot
V(g)$label_fg <- NA

for (i in c(1,2,3,4,5,8,12)){
  ok <- membership(fg) == i
  str_i <- as.character(i)
  V(g)$label_fg[ok] <- str_i
}

table(V(g)$label_fg)


# Plot graph with cluster label
top_nodes <- V(g)[order(-degree)][1:300]
small.g <- delete.vertices(g, which(!V(g) %in% top_nodes))
lay <- layout_with_fr(small.g)

small.g <- simplify(small.g)

plot(small.g, 
     vertex.size = 5,
     edge.arrow.size = 0.1, 
     edge.arrow.width = 0.3,
     vertex.label = V(small.g)$label_fg,
     vertex.label.cex = 0.4,
     vertex.color = V(small.g)$color,
     layout = lay)

mtext("Top 300 verticies by degree", side = 1)
```

Now I am interested in the discourse of those groups. More concretely, lets look into tweets published by each group members. To do that, lets save user_id of the groups. 
```{r, eval = TRUE}
# Group 1: 12, 2 -> red
# Group 2: 1, 4, 5, 8, 3 -> blue

# Store users id
# red part
ok <- (V(g)$label_fg == "12" | V(g)$label_fg == "2")
red <- V(g)$name[ok]
red <- red[!is.na(red)]
length(red)

# blue part
ok <- (V(g)$label_fg == "1" | 
         V(g)$label_fg == "4"|
         V(g)$label_fg == "5"|
         V(g)$label_fg == "8"|
         V(g)$label_fg == "3")
table(ok)
blue <- V(g)$name[ok]
blue <- blue[!is.na(blue)]
length(blue)

```

Let's save R objects for next part, creating a word cloud using Tweets.
```{r, eval = FALSE}
save(rigged, g, fg, red, blue, file = "rigged_election.RData")
```

## Exercise
Create a **reply network** of the rigged election data.

1. Create graph object containing reply network.
2. Find out top 10 users by indegree.
3. Find out top 10 users by outdegree.
4. Plot a reply network.