---
title: "Word cloud"
author: "Taehee Kim"
date: "12/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, eval = TRUE, message= FALSE}
library(dplyr)
library(wordcloud)
library(RColorBrewer)
library(tidytext)
library(SnowballC)

load("rigged_election.RData")
```

## Preperation
In this session, we create a word cloud of two goups we detected last session. To do that, we need to extract tweet texts of each group members. Since some of user's texts are stroed in retweet related columns, I create a new dataframe which contain all original tweets as a first step. 

```{r, eval = TRUE}


fields <- c("user_id", "status_id", "created_at", "screen_name", "text", "retweet_count", 
            "is_retweet", "is_quote", "reply_to_user_id")

fields_rt <- c("retweet_user_id", "retweet_status_id", "retweet_created_at", 
               "retweet_screen_name", "retweet_text", "retweet_retweet_count")


tweets <- rigged %>%
  select(all_of(fields)) %>% # When you write select(fields), you get a warning message.
  filter(is_retweet == FALSE) %>% # Remove retweets
  filter(is_quote == FALSE) %>% # Remove quotes
  filter(is.na(reply_to_user_id) == TRUE) %>% # Remove replies
  select(-c(is_retweet, is_quote, reply_to_user_id)) # Remove columns we don't need anymore

head(tweets)

tweets_rt <- rigged %>%
  select(all_of(fields_rt)) %>%
  filter(is.na(retweet_user_id) == FALSE) # remove if retweet_user_id is NA

head(tweets_rt)

names(tweets_rt) <- names(tweets) # change names of columns of tweets_rt to bind two data.frame.

all_tweets <- bind_rows(tweets, tweets_rt)
dim(all_tweets)

all_tweets <- distinct(all_tweets, status_id, .keep_all = TRUE) # Remove duplicated ones.
dim(all_tweets)


# Check tweet text
trump <- all_tweets %>%
  filter(screen_name == "realDonaldTrump")
trump$text

sanders <- all_tweets %>%
  filter(screen_name == "BernieSanders")
sanders$text


# Find red group's tweets
red_tweets <- all_tweets %>%
  filter(user_id %in% red)

blue_tweets <- all_tweets %>%
  filter(user_id %in% blue)

dim(red_tweets)
dim(blue_tweets)

```

## Plotting word cloud
Now let's create a word cloud. To do that, we first need to clean up tweet texts. Following example demonstrates cleaning tweets text using regular expression and `gsub()` function. `gsub()` function replace all the matches of a pattern from a string. `gsub(pattern, replacement, string)`.

```{r, eval = TRUE}

# A function for cleaning tweet text
clean_tweet <- function(tweet_df){
  text <- tweet_df$text
  text <- gsub("https\\S*", "", text)  # remove https
  text <- gsub("@\\S*", "", text) # remove screen_name
  text <- gsub("[\n]", "", text) # remove line breaks
  text <- gsub("[[:punct:]]", "", text) # remove punctuation
  return(text)
}

```


First, we plot word cloud of the blue group.
```{r, eval=TRUE}
# Clean text
blue_tweets$text <- clean_tweet(blue_tweets)


tweets_words <- blue_tweets %>%
  select(text) %>%
  unnest_tokens(word, text) # Tokenization: break the text into individual tokens

head(tweets_words)

tweets_words <- tweets_words %>%
  anti_join(stop_words) # remove stop words: a commonly used word (eg., a, the, that) that does not give us much information 

words <- tweets_words %>%
  count(word, sort = TRUE)

head(count)

set.seed(3)
wordcloud(words = words$word, 
          freq = words$n, 
          random.order = FALSE, 
          rot.per = 0.35,
          colors = brewer.pal(8, "Dark2"), 
          scale = c(4,0.5), 
          min.freq = 5)
```

### Exercise
(1) Plot word cloud of `red` group.

(2-1) Plot word cloud using Donald Trump's recent tweets.

(2-2) Plot word cloud using Joe Biden's recent tweets.

(2-3) Compare the results.

## BONUS: Stemming
```{r, eval = TRUE}
# Stemmed version

tweets_words <- blue_tweets %>%
  select(text) %>%
  unnest_tokens(word, text)

tweets_words <- tweets_words %>%
  anti_join(stop_words)

words <- tweets_words %>%
  mutate(stem = wordStem(word)) %>%
  count(stem, sort = TRUE)

set.seed(5)
wordcloud(words = words$stem, freq = words$n, random.order = FALSE, rot.per = 0.35,
          colors = brewer.pal(8, "Dark2"), scale = c(4,0.5), min.freq = 5)

```

